DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-08-01 2015CompleteDerivation/completeDerivation.tex
Add math for the classical uncertainty principle
Adding a figure

@@

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{calculator}
\usepackage{standalone}

@@

\begin{figure}
	\includestandalone[width=\columnwidth]{pictures/independentDof}
	\caption{The metric $\omega$ and its components along two independent degrees of freedom. As we change state variables, the components are still orthogonal to each other. Note: this is a 2D conceptualization of what happens in 4D.}
	\label{fig:independent_dof}
\end{figure}

@@

\section{Prelude to quantum}

\subsection{Classical uncertainty principle}

\begin{align*}
L = &\int (q-\mu_q)^2 \rho \, dqdp \int (p-\mu_p)^2 \rho \, dqdp \\
&+ \lambda_1(\int \rho dqdp - \rho_{tot})\\
&+ \lambda_2(- \int \rho \ln \rho \, dqdp - H_0)\\
\delta L = &\int \delta \rho [(q-\mu_q)^2 \sigma_p^2 + \sigma_q^2 (p-\mu_p)^2 \\ &+ \lambda_1 + \lambda_2 \ln \rho + \lambda_2 ] dqdp = 0 \\
\rho = &\frac{\rho_{tot}}{ \sqrt{4 \pi ^2\sigma_q^2\sigma_p^2}} e^{-\frac{(q-\mu_q)^2(p-\mu_p)^2}{4\sigma_q^2\sigma_p^2}} \\
= &\frac{\rho_{tot}}{e^{H_0 - 1}} e^{-\frac{\pi ^2(q-\mu_q)^2(p-\mu_p)^2}{\exp (2(H_0 - 1))}}
\end{align*}
\begin{align*}
\sigma_q\sigma_p \geq \exp (H_0 - 1) / 2 \pi 
\end{align*}
